Command line programs from LatticeRepLib

### 2023-01-09 C3/C3.tex
testing and update .gitignore
test
just testing
continuing work on command line program writeup
improving formatting mostl

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

%xxxxxx just for testing github % 2

@@

	In \CIII{}, in terms of the Delone scalars, 
	a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932} (see~\citeasnoun{andrews2019a}).
	As a memonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).

>>>>

%xxxxxx just for testing github % 2
%xxxxxx just for testing github % 3

\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

@@

	In \CIII{}, in terms of the Delone scalars, 
	a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932} (see~\citeasnoun{andrews2019a}).
	As a mnemonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).

### 2023-01-09 ProgramSummary/ProgramSummary..tex
improving formatting mostl

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{xtabular]
%\usepackage{bm}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\BIV}[0]{$\bf{B^{4}}$}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\DXIII}[0]{$\bf{D^{13}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

\begin{document}                  % DO NOT DELETE THIS LINE

@@

	% The title of the paper. Use \shorttitle to indicate an abbreviated title
	% for use in running heads (you will need to uncomment it).
	{\LARGE \emph{\today}} \\
	\title{Command line programs from LatticeRepLib}
	\shorttitle{Command line programs}

@@

	\newcommand{\ci}[0]{$c_1$}
	\newcommand{\cii}[0]{$c_2$}
	\newcommand{\ciii}[0]{$c_3$}

@@

	\section{Data Inputs:}

	\begin{table}
		\caption{	All these are case-insensitive. If a particular
			input lattice is invalid, it is rejected with a message.}
		\begin{tabular}{l p{.2\textwidth} l l l}
			\toprule

@@

			\textbf{Crystal Lattice Input:} 
			``\textbf{A}'', ``\textbf{B}'', ``\textbf{C}'', ``\textbf{P}'', ``\textbf{R}'', ``\textbf{F}'', ``\textbf``{I}''	\\
			~~~~~followed by three axis lengths and three angles (in degrees)\\
			\underline{\textbf{semicolon}}: 
			lines beginning with a semicolon are treated as comments\\
			\underline{\textbf{END:}} ends the data input section\\
			\bottomrule
		\end{tabular}

@@

	\begin{table}
		\caption{Programs for convert lattice representations}
		\begin{tabular}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\toprule
			Name&	in&	out&	param& Output	\\
			\midrule
			CmdToB4&	y&	\BIV{}&&		For each input, 
			it produces the 4 vectors as a,b,c,d as E3 vectors, 
			and also the lengths of each of those vectors.\\[.9pt]
			CmdToC3&	y&	\CIII{}&&		
			For each input, produces the \CIII{} representation in the form 
			(\#,\#) (\#,\#) (\#,\#), 
			which does not conform to the format for input to other programs.\\[.9pt]
			CmdToCell&	y&	a,b,c,$\alpha$,$\beta$,$\gamma$&&		
			Converts to the conventional unit cell representation.\\[.9pt]
			CmdToD13&	y&	\DXIII{}&&		
			Outputs the lengths of the 13 unique vectors describing the Dirichlet cell.\\[.9pt]
			CmdToDC&	y&	y		\\[.9pt]
			CmdToG6&	y&	\GVI{}&&		Converts the input to \GVI{}\\[.9pt]
			CmdToS6&	y&	\SVI{}&&		Converts the input to \SVI{}\\[.9pt]
			\bottomrule

@@

		\begin{table}
		\caption{Summary of programs manipulating data}
		\begin{tabular}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\toprule
			Name&	in&	out&	param& Output	\\
			\midrule
			CmdCmplx&	NA&	y&&Currently, this just outputs some 
			programmed examples.		\\[.9pt]
			CmdDelone&	y&	\SVI{}&&Converts input to\SVI{}		\\[.9pt]
			CmdGen&	NA&	\GVI{}&	ngen& - number of examples to generate (optional)\\
			{}&&&type - &lattice type to generate, many options (optional) 
			c,t,h,o,r,h,m,a, 
			cP, cF,cI, tP, tI, hP, hR, oP, oF, oI, oS, mP, mC, mS, aP, 
			numeric Niggli types - 1-44, 
			Delone types - C1,C3,C5,~\dots 
			If no parameters are present, one each of the 44 Niggli types. 
			If only a number is present, that is how many of each of the 44 Niggli types to generate.
			For usage examples, see Table \ref{CMDGENexamples}\\[.9pt]
					CmdLM&	y&	cy&&		Lattice Matching. 
			The first input cell is used as the reference. 
			Succeeding cells are matched 
			as well as possible to the reference cell.\\[.9pt]
			CmdNiggli&	y&	\GVI{}&&		Produces the Niggli reduced cell for each input\\[.9pt]
			CmdPath&	?&	? && Clearly not working the way it should		\\[.9pt]
			CmdPerturb&	y&	y&	n-number of perturbations, parts per thousand to perturb&
			n cells perturbed normal to the input \SVI{} vector
			If a lattice centering (including P) is input,
			the output is in the same centering. Otherwise, the output is in \SVI{}.	\\[.9pt]
			CmdS6Refl&	y&	\SVI{}&	&	For each input, 
			all 24 \SVI{} reflections are produced.\\[.9pt]
			CmdSella&	y&	y		\\[.9pt]
			CmdSort&	y&	y&	"C3" or "seq'&	\\[.9pt]
			CmdVolume&	y&	mod&&		Outputs the unit cell and the volume of each input cell.\\[.9pt]
			MultiMetricDists&	y& mod&"Y/y"(optional)&	Parameter Y/y for maxima style output		\\[.9pt]
			PlotC3&	y&	mod& 
			1,2,or 3 for which \CIII{} coordinate to plot. 
			"seq" or "C3"& Plot one of the 3 \CIII{} coordinates, 
			sorted by minimizing point to point distance 
			for \SVI{}{ reflections or 
				sorting the \CIII{} components to put them 
				in the asymmetric unit.}	\\[.9pt]
			Radial&	y&	as radial	&&	
			Radial computes the polar distances in Angstroms 
			from the first input cell. 
			That is {a,$\alpha$}, {b,$\beta$}, and {c,$\gamma$} 
			as coordinates in complex space.\\[.9pt]
			SELLA&	y&	mod&&	
			Outputs the distances from each of the Bravais lattice types 
			(in \svi{}).	\\[.9pt]
			SVD&	y&	mod&& Outputs the singular value decomposition vectors
			and eigenvalues for the input lattice. This is done in \SVI{}.		\\[.9pt]			
			\bottomrule

@@

@@

\begin{itemize}
	\item Niggli types by number 1-44 (see Table \ref{NiggliFormsI}).
	\item Delone types by Delone's designation - 
	C1,C3,C5, T1, T2, T5, R1, R3,\\ 
	O1A, O2, O3, O4, O5, O1B, M1A, M2A, M3, M4, M1B, M2B, 
	A1, A2, A3, H4 (see Table \ref{s6table}).
	\item Crystal system - c,h,t,o,m,a
\end{itemize}

On input to a number of lattices, 
SVD calculates a Singular Value Decomposition.
The output consists of the eigenvalues and 
the six eigenvectors.
It is important to check that the form of
each cell is the same; for instance, monoclinic
cell should have the unique interaxial angle
in the same place (\textit{e.g.} $\beta$)

\textbf{Command line:}\\
CmdGen 5 33 | CmdSort seq | SVD\\
; SVD\\
S6 from input cell   0.000 -31.196   0.000 -71.963 -109.653 -131.880\\
S6 from input cell   0.000 -23.060   0.000 -77.367 -110.398 -125.599\\
S6 from input cell   0.000 -28.898   0.000 -54.985 -106.336 -82.229\\
S6 from input cell   0.000 -56.133   0.000 -103.736 -177.343 -123.204\\
S6 from input cell   0.000 -10.111   0.000 -50.618 -91.57100 -98.102\\

\textbf{eigenvalue     0}         vector         1 0 0 0 0 0\\
eigenvalue 413.012       vector         0 -0.1728 00 -0.4007 -0.6616 -0.6097\\
eigenvalue 48.3869       vector         0 -0.4009 0 -0.1129 -0.5164 0.7482\\
eigenvalue 14.0785       vector         0 -0.7060 0 -0.4581 0.5344 -0.0786\\
eigenvalue 8.53435       vector         0 0.5576 0 -0.7853 0.1001 0.2494\\
\textbf{eigenvalue     0}         vector         0 0 -1 0 0 0

@@

@@

	The $C^{++}$ ~code for C++ is available in github.com, in
	\url{https://github.com/duck10/LatticeRepLib.git}.

>>>>

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{xtabular]
%\usepackage{bm}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
 \usepackage{setspace}
 \DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\BIV}[0]{$\bf{B^{4}}$}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\DXIII}[0]{$\bf{D^{13}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

\DeclareMathOperator{\mr}{\textfrak{P}_i}
\begin{document}                  % DO NOT DELETE THIS LINE
	\singlespacing
	$\mr$

@@

	% The title of the paper. Use \shorttitle to indicate an abbreviated title
	% for use in running heads (you will need to uncomment it).
	{\Large PDF generated: \emph{\today}} \\
	\title{Command line programs from LatticeRepLib}
	\shorttitle{Command line programs}

@@

	\newcommand{\ci}[0]{$c_1$}
	\newcommand{\cii}[0]{$c_2$}
	\newcommand{\ciii}[0]{$c_3$}
	\begin{abstract}
	\end{abstract}

@@

	\section{Data Inputs:}
	\subsection{Table of input types}

	In general, there are 5 types of input lines, see Table \ref{inputtypes}.
	Except for "END", they can be combined in any order.

	\begin{table}
		\label{inputtypes}
		\caption{	All these are case-insensitive. If a particular
			input lattice is invalid, it is rejected with a message.}
		\begin{tabular}{l p{.2\textwidth} l l l}
			\toprule

@@

			\underline{\textbf{Crystal lattice input:}} 
			``\textbf{A}'', ``\textbf{B}'', ``\textbf{C}'', ``\textbf{P}'', ``\textbf{R}'', ``\textbf{F}'', ``\textbf``{I}''	\\
			~~~~~followed by three axis lengths and three angles (in degrees)\\
			\underline{\textbf{semicolon}}: 
			lines beginning with a semicolon are treated as comments\\
			\underline{\textbf{END:}} ends the data input section\\
			\bottomrule
		\end{tabular}

@@

	\subsection{Filters - change lattice representation}

	\begin{table}
		\renewcommand{\arraystretch}{1.2}
		\caption{Programs to convert lattice representations}
		\begin{tabular}{l l l p{.7\textwidth}  l}
			\toprule
			Name		&	in	&	out				& Output	\\
			\midrule
			CmdToB4		&	y	&	\BIV{}		&		For each input, 
			it produces the 4 vectors as a,b,c,d as E3 vectors, 
			and also the lengths of each of those vectors.\\[.9pt]
			CmdToC	3	&	y	&	\CIII{	}	&		
			For each input, produces the \CIII{} representation in the form 
			(\#,\#) (\#,\#) (\#,\#), 
			which does not conform to the format for input to other programs.\\[.9pt]
			CmdToCell	&	y	&	
			\parbox[t]{0.07\textwidth}{${	a,b,c,}$ \\ ${\alpha,\beta,\gamma}$}		&		
			Converts to the conventional unit cell representation.\\[.9pt]
			CmdToDC		&	y	&	\DXIII{}		&	Outputs the lengths of the 13 unique vectors describing the Dirichlet cell.\\[.9pt]			
			CmdToG6		&	y	&	\GVI{}		&		Converts the input to \GVI{}\\[.9pt]
			CmdToS6		&	y	&	\SVI{}		&		Converts the input to \SVI{}\\[.9pt]
			Radial		&	y	&	Polar	&
				CSomputes the polar distances in Angstroms 
				from the first input cell. 
				That is {(a,$\alpha$)}, {(b,$\beta$)}, and {(c,$\gamma$)} 
				as coordinates in complex space.\\[.9pt]
			\bottomrule

@@

\subsection{Data processing programs}

		\begin{longtable}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\caption{Summary of programs manipulating data}
			\label{processingprogs}\\ %NOTE: that lineskip is necessary to prevent toprule from crashing
			\toprule
			Name		&	in	&	out		&	\begin{parbox}[t]{2cm}{
				command line\\
				param{s}}
			\end{parbox}	& Output	\\
			\midrule
			CmdCmplx	&	NA	&	y		&\hrulefill	&Currently, 
				this just outputs some programmed examples.		\\[.9pt]
			CmdDelone	&	y	&	\SVI{}	&\hrulefill	&Converts input to \SVI{}		\\[.9pt]
			CmdGen		&	NA	&	\GVI{}	&	ngen - number of examples to generate (optional)\\
				{}		&		&			&type		& - lattice type to 
				generate, many options (optional) 
				c,t,h,o,r,h,m,a, 
				cP, cF,cI, tP, tI, hP, hR, oP, oF, oI, oS, mP, mC, mS, aP, 
				numeric Niggli types - 1-44, 
				Delone types - C1,C3,C5,~\dots 
				If no parameters are present, one each of the 44 Niggli types. 
				If only a number is present, that is how many of each of the 44 Niggli types to generate.
				For usage examples, see Table \ref{CMDGENexamples}\\[.9pt]
			CmdLM		&	y	&	y		&	\hrulefill		&		Lattice Matching. 
				The first input cell is used as the reference. 
				Succeeding cells are matched 
				as well as possible to the reference cell.\\[.9pt]
			CmdNiggli	&	y	&	\GVI{}	&\hrulefill	&		
				Produces the Niggli reduced cell for 	each input\\[.9pt]
			CmdPath		&	?	& ?			&\hrulefill	& Clearly not working the way it should		\\[.9pt]
			CmdPerturb	&	y	& y			&	n-number of perturbations,

				parts per thousand to perturb			&
				n cells perturbed normal to the input \SVI{} vector
				If a lattice centering (including P) is input,
				the output is in the same centering. Otherwise, the output is in \SVI{}.	\\[.9pt]
			CmdS6Refl	&	y	&	\SVI{}	&\hrulefill	&	For each input, 
				all 24 \SVI{} reflections are produced.\\[.9pt]
			CmdSella	&	y	&	y		&\hrulefill	&
				SELLA produces 2 output: std::out contains the match of
				each of the 24 Delone types; SVG for the Grimmer
				diagram is written to a file with a name such as 
					\verb#SEL__2023-01-07.08_56_42.svg# with date/time stamp.\\
			CmdSort		&	y	&	y		&"C3" or "seq'&	\\[.9pt]
			CmdVolume	&	y	&	mod		&\hrulefill	&		Outputs the unit cell 
				and the volume of each input cell.\\[.9pt]
			MultiMetricDists&y	& mod		&"Y/y"(optional)&	
				Parameter Y/y for maxima style output		\\[.9pt]
			PlotC3		&	y	&	mod		& 			& Plot 
				the three \CIII{} coordinates\\[.9pt]
			SELLA		&	y	&	mod		&\hrulefill	&	
				Outputs the distances from each of the Bravais lattice types 
				(in \svi{}).	\\[.9pt]
			SVD			&	y	&	mod		&\hrulefill	& Outputs the singular value decomposition vectors
				and eigenvalues for the input lattice. This is done in \SVI{}.		\\[.9pt]			
			\bottomrule

		\end{longtable}
%	\end{table}

@@

	\subsection{Individual program details}

@@

\begin{itemize}
	\item Niggli types by number 1-44 (see Table \ref{NiggliFormsI}).
\begin{singlespace}
		\item Delone types by Delone's designation - 
	C1,C3,C5, T1, T2, T5, R1, R3,\\ 
	O1A, O2, O3, O4, O5, O1B, M1A, M2A, M3, M4, M1B, M2B, 
	A1, A2, A3, H4 (see Table \ref{s6table}).
\end{singlespace}
	\item Crystal system - c,h,t,o,m,a
\end{itemize}

@@

	On input to a number of lattices, 
	SVD calculates a Singular Value Decomposition.
	The output consists of the eigenvalues and 
	the six eigenvectors.
	It is important to check that the form of
	each cell is the same; for instance, monoclinic
	cell should have the unique interaxial angle
	in the same place (\textit{e.g.} $\beta$)\\

	\begin{samepage}
		{\nopagebreak{
				\textbf{Command line:}\\
				CmdGen 5 33 | CmdSort seq | SVD\\
				; SVD\\
				S6 from input cell   0.000 -31.196   0.000 -71.963 -109.653 -131.880\\
				S6 from input cell   0.000 -23.060   0.000 -77.367 -110.398 -125.599\\
				S6 from input cell   0.000 -28.898   0.000 -54.985 -106.336 -82.229\\
				S6 from input cell   0.000 -56.133   0.000 -103.736 -177.343 -123.204\\
				S6 from input cell   0.000 -10.111   0.000 -50.618 -91.57100 -98.102\\
			}
		}
	\end{samepage}

	\begin{samepage}
		\nopagebreak{
			\textbf{Output}:\\
			\textbf{eigenvalue     0};         vector         1 0 0 0 0 0\\
			eigenvalue 413.012;       vector         0 -0.1728 00 -0.4007 -0.6616 -0.6097\\
			eigenvalue 48.3869;       vector         0 -0.4009 0 -0.1129 -0.5164 0.7482\\
			eigenvalue 14.0785;       vector         0 -0.7060 0 -0.4581 0.5344 -0.0786\\
			eigenvalue 8.53435;       vector         0 0.5576 0 -0.7853 0.1001 0.2494\\
			\textbf{eigenvalue     0};         vector         0 0 -1 0 0 0
		}
	\end{samepage}

@@

	The $C^{++}$ ~code is available in github.com, in
	\url{https://github.com/duck10/LatticeRepLib.git}.
